Hypertension and microbiome

### 2019-05-15 articletwo.Rmd
Typo

adjmean.lacto.saltgroup <- predict(lm.lacto.saltgroup,
                               df.genus.salt.unadjusted,
                               interval = "confidence") %>%
    as.data.frame %>%
    dplyr::rename(estimate = fit,
                  conf.low = lwr,
                  conf.high = upr) %>%
    rownames::tibble_to_column("term")
```

@@

```{r table map lactobacillus}
gvlma.table.plot(lm(log(MAP) ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$table %>% kable
```

>>>>

adjmean.lacto.saltgroup <- predict(lm.lacto.saltgroup,
                               df.genus.salt.unadjusted,
                               interval = "confidence") %>%
    as.data.frame %>%
    dplyr::rename(estimate = fit,
                  conf.low = lwr,
                  conf.high = upr) %>%
    tibble::rownames_to_column("term")
```

@@

```{r table map lactobacillus}
gvlma.table.plot(lm(MAP ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$table %>% kable
```
